LOSD: A Linked Open Social Dataset for Scientific Benchmarking

### 2019-07-01 mdpi/template.tex
acrescentado sobre virtual ethnography

\subsection{Data acquisition}\label{acq}
Research involving human subjects raise well-known ethical issues,
although ethical regulation for (non-medical) research in social systems is not always endorsed by scientists~\cite{eth}.
Furthermore, the online social networking platforms often restrict access
to the data and user may consider illegal the use of their data through web crowlers~\cite{ile1,ile2,ile3}.
Although Twitter and GMANE (email) data is available through public APIs,
the other sources are more problematic.
In this context, research using data, e.g. from Facebook, is precarious
if not prohibited.
We reached a potential solution to this issue through continuated research with
collaborators in the fields of phylosophy, social sciences, antropology and psychology.
The conceptual framework is presented in~\cite{antphy,antphy2}, and in essence
consists in researching first the social networks related to the researchers,
and keeping the procedures, data, algorithms and results publicly available.
These practices enabled collecting and sharing the data in LOSD,
and was called ``Anthropological Physics'' because it relies in the
etnographic tecnique of investigating the social structures
by studying the researcher, as to ammeliorate the ethic issues.
Accordingly, aside from the data acquired from Twitter, all data in LOSD
was gathered from social instances where the first author is a participant.
For example, all Facebook ego networks were donated to the first author by
users which know him and were interested in his research and intervention on the networks,
and all email and Facebook groups data was obtained from groups where the first author is a member.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\funding{This research was funded by CNPq (grant number XXX) and FAPESP (grant number ).}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
\appendixtitles{no} %Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
\appendix
\section{}
\unskip
\subsection{}
The appendix is an optional section that can contain details and data supplemental to the main text. For example, explanations of experimental details that would disrupt the flow of the main text, but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data is shown in the main text can be added here if brief, or as Supplementary data. Mathematical proofs of results not central to the paper can be added as an appendix.

\section{}
All appendix sections must be cited in the main text. In the appendixes, Figures, Tables, etc. should be labeled starting with `A', e.g., Figure A1, Figure A2, etc.

>>>>

\subsection{Data acquisition}\label{acq}
Research involving human subjects raise well-known ethical issues,
although ethical regulation for (non-medical) research in social systems is not always endorsed by scientists~\cite{eth}.
Furthermore, the online social networking platforms often restrict access
to the data and user may consider illegal the use of their data through web crowlers~\cite{ile1,ile2,ile3}.
Although Twitter and GMANE (email) data is available through public APIs,
the other sources are more problematic.
In this context, research using data, e.g. from Facebook, is precarious
if not prohibited.
We reached a potential solution to this issue through continuated research with
collaborators in the fields of phylosophy, social sciences, antropology and psychology.
The conceptual framework is presented in~\cite{antphy,antphy2}, and in essence
consists in researching first the social networks related to the researchers,
and keeping the procedures, data, algorithms and results publicly available.
These practices enabled collecting and sharing the data in LOSD,
and was called ``Anthropological Physics'' because it relies in the
etnographic tecnique of investigating the social structures
by studying the researcher, as to ammeliorate the ethical issues
(not to be confused e.g. with ``virtual ethnography''~\cite{veth}).
Accordingly, aside from the data acquired from Twitter, all data in LOSD
was gathered from social instances where the first author is a participant.
For example, all Facebook ego networks were donated to the first author by
users which know him and were interested in his research and intervention on the networks,
and all email and Facebook groups data was obtained from groups where the first author is a member.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\funding{This research was funded by CNPq (grant 14068/2013-4) and FAPESP (grant 2017/05838-3).}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
% \appendixtitles{no} %Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
% \appendix
% \section{}
% \unskip
% \subsection{}
% The appendix is an optional section that can contain details and data supplemental to the main text. For example, explanations of experimental details that would disrupt the flow of the main text, but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data is shown in the main text can be added here if brief, or as Supplementary data. Mathematical proofs of results not central to the paper can be added as an appendix.
% 
% \section{}
% All appendix sections must be cited in the main text. In the appendixes, Figures, Tables, etc. should be labeled starting with `A', e.g., Figure A1, Figure A2, etc.
